
%\cleardoublepage

\addcontentsline{toc}{chapter}{Acknowledgements}

\begin{acknowledgements}

I would like to thank everyone who directly and indirectly contributed to the realisation of this Biostatistics MSc thesis.
First of all, my supervisor, Nuno for providing me with the opportunity to work, develop, and prepare my project and dissertation in the field of malaria epidemiology and modelling of infectious diseases.
Moreover, thank you for all the advises, ideas, and continuous constructive criticism (as well as all the Wednesdays afternoon football games) that have already proven to be valuable teachings to take into the future.
I also want to thank my co-supervisor, Marília, for all the Skype pep talks and helpful suggestions during the later stages of the dissertation that kept me motivated and helped to further improve the thesis.
I am grateful for the opportunity to prepare this project at two institutions.
First, the London School of Hygiene and Tropical Medicine (LSHTM). Particularly acknowledging all members from the Chris Drakeley's group, whom during my time abroad made me feel welcome to work in a specialised and fully dedicated research group. Cheers to you!
And second, the Faculty of Sciences at the University of Lisbon (FCUL), that alongside with the Erasmus+ programme allowed me to travel abroad and learn new research fields, amazing organisations, and terrific people.

E agora em português.
Quero agradecer a todos aqueles que me apoiaram no projecto e escrita da tese.
Um obrigado a toda a minha família, principalmente aos meus pais e irmãos por me ajudarem com as viagens para a frente e para trás ao longo deste ano, e por constantemente zelarem pelo meu bem estar.
Um beijo especialmente carinhoso à minha Mãe por todos os telefonemas, cartas e mimos que disponibilizou.
Logo que concluir esta tese, será a primeira a quem vou ligar.
Aos meus colegas de mestrado um muito obrigado.
Especialmente ao Bruno, Heloísa, e Sofia, por me terem ajudado a entrar ná área da estatística ao longo dos dois anos do mestrado; e ao Constantino, por todos os debates, explicações e demonstrações, e por não esperar menos do que o melhor de mim, ao fazer de criticar esta tese um passatempo.
Obrigado ainda à minha família alargada e aos mais variados amigos, que se preocuparam e me fizeram companhia ao longo do ano.

Mais que todos, mil obrigados à Dida, por tudo.
\\
Obrigado Formiguita.

\begin{flushright}
João Malato,\\
Lisboa, Outubro de 2018.\\
\end{flushright}

\end{acknowledgements}
